Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
foo

\subsubsection{Summary of Findings}

All users experienced using multiple web sites in order to complete a task, and felt that the lack of existing integration between sites hindered their ability to make informed choices. Participants felt that they did not include particular aspects of a decision because the process to investigate them would be too difficult or take too much time.

%People said that they would like a website that could support the evolution of an event, that allowed them to post drafts of an event.  They felt that organising an event should be a process that changes over time.  Three participants said that they would like a recommendation system for places to eat and activities.  Another strong requirement was that it had to be ubiquitous so that everyone could use it because they wanted a single place to communicate with their friends.  While Facebook was the most popular social networking site for organising events, half of the participants felt that it was not the best solution and would prefer a collaborative environment.

@@

\subsection{PS.2 - Technical Challenges of Data Integration}
Our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb - \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To increase the variety of sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2--5 sources from each, for a total of 20.

For each feed, 3--5 ``typical'' records of a single type were obtained; for social networking sites this was user profiles, for retail sites this was product info, etc.
%Records were located either by first querying for popular key terms using each site's keyword query API (if available), or a ``top products'' query if available.  
For each such data record, two simple complexity metrics were computed: the \emph{average width} and \emph{average depth}.  Determining the width required first finding the appropriate level for comparison; for example, Amazon's retail product ``Item'' root record had few attributes about the actual product compared to its ``ItemAttributes'' sub-property, which was used instead. The average depth was simply the mean depth to each leaf node from the chosen comparison level.
% This step was done manually, with an effort to select most similar components for comparison.  
% Depth was computed as the average number of levels from record root to leaves across all properties, and was measured, with width, to convey the overall size/complexity of each record.

@@

Just as the wise Italian in Voltaire's poem \emph{La Begueule} predicted,``the best is the enemy of the good'', we believe that the quest for complete approaches to data integration have perhaps caused more scruffy, ``ad-hoc'' approaches to be overlooked.  Based upon the results of our investigation, we believe that there are a number of advantages to user-driven data reconciliation over automatic to bespoke ones; specifically, this enables the user to combine data as part of his or her sensemaking process, using subjective judgement in the process

@@

Just as journalism became peer-produced with the explosion of blogging, data journalism is on the brink of moving from skilled data analysts the likes of The Guardian Datablog staff\footnote{Guardian Datablog - \url{http://www.guardian.co.uk/news/datablog}} into the hands of the ordinary citizen \footnote{Data Journalism Hand Book: \url{datajournalismhandbook.org}}.  In order for this to happen, however, tools that allow people to effectively combine data more effectively than current structured PIM tools and generic spreadsheet tools will become increasingly important.

>>>>

\subsubsection{Summary of Findings}
% TODO: how does this summary support the thesis of the paper?
People said that they would like a website that could support the evolution of an event, that allowed them to post drafts of an event.  They felt that organising an event should be a process that changes over time.  Three participants said that they would like a recommendation system for places to eat and activities.  Another strong requirement was that it had to be ubiquitous so that everyone could use it because they wanted a single place to communicate with their friends.  While Facebook was the most popular social networking site for organising events, half of the participants felt that it was not the best solution and would prefer a collaborative environment.

@@

\subsection{PS.2 - Technical Challenges of Data Integration}
Our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb - \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To increase the variety of sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2-5 sources from each, for a total of 20.

For each feed, 3-5 ``typical'' records of a single type were obtained; for social networking sites this was user profiles, for retail sites this was product info, etc.
%Records were located either by first querying for popular key terms using each site's keyword query API (if available), or a ``top products'' query if available.  
For each such data record, two simple complexity metrics were computed: the \emph{average width} and \emph{average depth}.  Determining the width required first finding the appropriate level for comparison; for example, Amazon's retail product ``Item'' root record had few attributes about the actual product compared to its ``ItemAttributes'' sub-property, which was used instead. The average depth was simply the mean depth to each leaf node from the chosen comparison level.
% This step was done manually, with an effort to select most similar components for comparison.  
% Depth was computed as the average number of levels from record root to leaves across all properties, and was measured, with width, to convey the overall size/complexity of each record.

@@

Just as the wise Italian in Voltaire's poem \emph{La Begueule} said that ``the best is the enemy of the good'', we believe that complete approaches to data integration have perhaps caused less principled, ``ad-hoc'' approaches to be overlooked.  Based upon the results of our investigation, we see a number of benefits to lightweight, user-driven approaches to coping with heterogeneity over automatic and bespoke ones. Just as the \emph{user-subjective approach} to PIM \cite{user-subjective} showed that subjective labels and attributes were more useful than physical ones for files and folders, a user-controlled approach to data integration, where data may be combined (and separated) at will may benefit the sensemaking or decision-making process.   Towards this end, our results of our pre-studies and DataPalette show that, for a majority of the kinds of structured data feeds available on the Web today, the kinds of heterogeneity can be largely managed using simple interactive approaches that are intuitive and preceived as useful by end-users.

%%  things as simple as coreference involved any subjective judgement,

@@

%% Just as journalism became peer-produced with the explosion of blogging, data journalism is on the brink of moving from skilled data analysts the likes of The Guardian Datablog staff\footnote{Guardian Datablog - \url{http://www.guardian.co.uk/news/datablog}} into the hands of the ordinary citizen \footnote{Data Journalism Hand Book: \url{datajournalismhandbook.org}}.  In order for this to happen, however, tools that allow people to effectively combine data more effectively than current structured PIM tools and generic spreadsheet tools will become increasingly important.
